MULTI process challenge : the FML solution

### 2021-04-29 5-Analysis.tex

any disambiguations of the  case  description and assumptions made, any potentially added require-ments

>>>>

any disambiguations of the  case  description and assumptions made, any potentially added requirements

quelles hypothèses supplémentaires ?

+ architecture de la modélisation (ce qui se trouve dans le ppt), le détail se retrouvera dans la section suivante

Joel commence
